\pagebreak
\section{Goals of the project}
% Give a short summary of the main objectives of the project and the expected
% results. Provide an overview of the report, chapter by chapter.

The main objective of the project is implementation a translator from Event-B
modeling language to Eiffel programming language as Rodin platform plugin.

\href{http://poporo.uma.pt/EventB2Java/EventB2Java.html}
{Like it already be done} by Nestor Catano and Victor Rivera for translation from
Event-B to Java (or JML), before me.

But in my case I should implement plugin which translate Event-B model to Eiffel
Programming Language.\\

As results of work should be delivered working plugin, case study
(\href{http://poporo.uma.pt/EventB2Java/EventB2Java_studies.html}{or studies})
model in Event-B, translation of this model to Eiffel and proves of soundness of
the translator.\\

Overview of the report:\\
\begin{enumerate}
\item \textbf{Overview of System Specification}
  - section describes development specifics for Rodin Platform.
 
\item \textbf{Background Theory}
  - section describes formal approach, Event-B methodology, Eiffel
  Programming Language. 

\item \textbf{Overview of Task Specification and Project Schedule}
  - section consider plugin development decomposition to tasks, schedule
  timings and so on.

\item \textbf{Review of Tasks}
  - section describes current status of tasks.

\item \textbf{Interim Results}
  - section describes interim results of thesis work.

\item \textbf{Short Term Plans}
  - section states next steps I will take in project.

\end{enumerate}
