\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}

\usepackage{graphicx}
\graphicspath{ {images/} }

\title{
	{Code Generation for Event-B}\\
	{\large Innopolis University}\\
	{\large \textsc{Interim report}}\\
}

\author{Georgiy Krikun}
\date{5 December 2016}
% ---------------------------------------------------------------------------
\begin{document}

\maketitle
\pagebreak
\begin{abstract}
  How about some other shit?
\end{abstract}

\pagebreak
\tableofcontents

\pagebreak

\section{Goals of the project}
Give a short summary of the main objectives of the project and the expected results.
Provide an overview of the report, chapter by chapter.

The main objective of the project is implementation of a translator from Event-B
modeling language to Eiffel programming language.

\section{Overview of the System Specification}
Provide an overview of the initial specification, setting out the main features of the
system or project and addressing at least system functionality, interfaces (electronic
and/or human), and signal/information representations.

\section{Background Theory}
Describe the essential theory or theories to be applied in the thesis.

\section{Overview of Task Specification and Project Schedule}
List the primary tasks and sub-tasks required to carry out the project and an overview
of the project schedule, giving the timings (start date, duration, amount of effort) of
each task. List and discuss any changes that have been made to the initial
specification of the project.

\section{Review of Tasks}
Provide a comprehensive review of the status of each task and sub-task, setting out at
least:
  The status (not started, on-going, complete, behind schedule, ahead of schedule ...);
  Problems encountered and identified solutions;
  Anticipated problems and possible solutions;
  Impact on the project schedule.

\section{Interim Results}
If possible, provide examples of any interim results you have achieved.

\section{Short Term Plans}
Identify the next steps you will take in the project.

\end{document}
